Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-02-25 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
new image

@@

>>>>

source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix <0.05))
valores_menores_que_0_05 <- sum(p_values_matrix < 0.05)
cat("Número de valores menores que 0.05:", valores_menores_que_0_05, "\n")

@@

source("../imagematrix.R")
hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.1))
```

### 2024-02-25 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
new image

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
We used $7 \times 7$ local sliding windows for the test. 
In Fig. \ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width = c("40mm", "60mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
knitr::include_graphics("../../../Figures/PDF/color7x7.pdf")

>>>>

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
We used $7 \times 7$ local sliding windows for the test. 
In Fig. \ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width = c("40mm", "60mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
knitr::include_graphics("../../../Figures/PDF/pvalues_7x7_col.pdf")
